\textbf{Too Beautiful to be Fake: Attractive Faces are Less Likely to be Judged as Artificially Generated}

### 2022-09-13 analysis.Rmd
start results

df <- df |>
  filter(!Stimulus %in% extreme_items$Stimulus)
```

@@

```{r message=FALSE, warning=FALSE, fig.height=fig.width*1.5}
# plot(estimate_density(filter(df, Participant == "60dd7b03f1e72d38230df476_9yh9n")$Belief_Answer))
df |>
  mutate(Participant = fct_relevel(Participant, df |>
    group_by(Participant) |>
    summarize(Belief_Answer = mean(Belief_Answer)) |>
    ungroup() |>
    arrange(Belief_Answer) |>
    pull(Participant) |>
    as.character())) |>
  # mutate(Participant = fct_relevel(Participant, as.character(dfsub$Participant))) |>
  ggplot(aes(x = Belief_Answer, y = Participant, fill = Participant)) +
  ggdist::stat_slab(scale = 2, slab_alpha = 0.9, normalize = "groups", color = "black", size = 0.1) +
  geom_vline(xintercept = 0, linetype = "dotted") +
  scale_y_discrete(expand = c(0.02, 0)) +
  scale_x_continuous(
    limits = c(-1, 1),
    expand = c(0, 0),
    breaks = c(-0.95, 0, 0.95),
    label = c("Fake", "", "Real")
  ) +
  scale_fill_viridis_d() +
  labs(x = "Simulation Monitoring", y = "Participants", title = "Distribution of Reality Judgments") +
  guides(fill = "none") +
  see::theme_modern() +
  theme(
    axis.text.y = element_blank(),
    plot.title = element_text(face = "bold", hjust = 0.5)
  ) +
  ggside::geom_xsidedensity(fill = "grey", color = "white") +
  ggside::scale_xsidey_continuous(expand = c(0, 0))
```

@@

parameters::parameters(model)
```

>>>>

df <- df |>
  filter(!Stimulus %in% extreme_items$Stimulus)

extreme_items
```

@@

```{r message=FALSE, warning=FALSE, fig.height=fig.width*1.5}
# plot(estimate_density(filter(df, Participant == "60dd7b03f1e72d38230df476_9yh9n")$Belief_Answer))
df |>
  mutate(Participant = fct_relevel(Participant, df |>
    group_by(Participant) |>
    summarize(Belief_Answer = mean(Belief_Answer)) |>
    ungroup() |>
    arrange(Belief_Answer) |>
    pull(Participant) |>
    as.character())) |>
  # mutate(Participant = fct_relevel(Participant, as.character(dfsub$Participant))) |>
  ggplot(aes(x = Belief_Answer, y = Participant, fill = Participant)) +
  ggdist::stat_slab(scale = 2, slab_alpha = 0.9, normalize = "groups", color = "black", size = 0.1) +
  geom_vline(xintercept = 0, linetype = "dotted") +
  scale_y_discrete(expand = c(0.02, 0)) +
  scale_x_continuous(
    limits = c(-1, 1),
    expand = c(0, 0),
    breaks = c(-0.95, 0, 0.95),
    label = c("Fake", "", "Real")
  ) +
  scale_fill_viridis_d() +
  labs(x = "Simulation Monitoring", y = "Participants", title = "Distribution of Reality Judgments") +
  guides(fill = "none") +
  see::theme_modern() +
  theme(
    axis.text.y = element_blank(),
    plot.title = element_text(face = "bold", hjust = 0.5)
  ) +
  ggside::geom_xsidedensity(fill = "grey", color = "white") +
  ggside::scale_xsidey_continuous(expand = c(0, 0))

df |> 
  group_by(Participant, Belief) |> 
  summarize(n = n() / 108, 
            Confidence = mean(Belief_Confidence)) |> 
  pivot_wider(values_from=c("n", "Confidence"), names_from="Belief") |> 
  ungroup() |> 
  describe_posterior(centrality = "mean", test=FALSE)
```

@@

hdi(df$Delay)
estimate_relation(model, at="Delay=c(0, 60)")

parameters::parameters(model, effects="fixed", exponentiate=TRUE)
parameters::parameters(m_conf, effects="fixed")
```

### 2022-09-13 submission/manuscript.Rmd
start results

@@

@@

>>>>

### Data Analysis

The real-fake ratings were converted into two scores.

@@

The analysis was carried out using *R 4.2* [**REF**], the *tidyverse* [**REF**], and the *easystats* collection of packages [**REFs for insight, parameters, performance, see**].

### Manipulation Check

Only one image file, classified as fake in 87.4\% of trials, yielded a strong simulation monitoring bias (> 85\%). This image was removed from further analysis (leaving 108 trials per participant). On average, across participants, 44\% of trials (95\% CI [0.11, 0.64]) was considered fake and 56\% of trials (95\% CI [0.36, 0.89]) was considered real.

There was a significant negative effect of the delay of re-exposure (with 95\% of values between 1.58 and 30.31 min), suggesting that shorter delays were associated with a slight bias towards the belief of reality (60\% at a theoretical delay of 0), which decreased to 50\% at a theoretical delay of 60 min ($OR = 0.99$, $95\% CI = [0.99, 1.00]$ $z = -2.27$, $p = 0.023$). There was also a significant negative effect on judgment confidence, but only in the real condition ($\beta = -0.005$, $95\% CI = [-0.1, 0.0]$, $p = .023$).

### Determinants of Simualtion Monitoring

@@

Although expected, the first striking result is that despite all items being real photos from the same database, all people easily believe (to high degrees of confidence) that a significant proportion of them was fake. This is a testimony to the existing expectations regarding CGI technology, as much as to the volatility of our sense of reality.
